### 2015-05-23 results.tex
change ping value to avg
ping comparison
raw results, tls benchmark

@@

@@

@@

\begin{figure}[ht]
\input{graphs/ftp-bench-comparison}
\caption{Comparison of file transfer methods. The background stripped bars are the CPU usage.}{}
\label{fig:ftp-bench-comparison}
\end{figure}

>>>>

\begin{figure}[ht]
\center
\input{graphs/openvpn-tls-bench}
\caption{TLS connections per second}{The background stripped bars are the CPU usage. Raw data in table~\ref{tab:tls-con}.}
\label{fig:openvpn-tls-bench}
\end{figure}

@@

\begin{figure}[ht]
\input{graphs/openvpn-ping-benchmark}
\caption{Ping min/avg/max response time}{for different packet sizes using OpenVPN}
\label{fig:ping-benchmark-openvpn}
\end{figure}

@@

\begin{figure}[ht]
\input{graphs/ping-bench-comparison}
\caption{Ping average comparison}{All values are for aes-256-cbc with sha-256}
\label{fig:ping-benchmark-comparison}
\end{figure}

@@

\begin{figure}[ht]
\input{graphs/ftp-bench-comparison}
\caption{Comparison of file transfer methods}{The background stripped bars are the CPU usage.}
\label{fig:ftp-bench-comparison}
\end{figure}
